\mysection{Polyhedral maps}\label{sec:polymap}

Since we want to state general {\sc Eberhard}-like theorems not only on polyhedra, i.e. the sphere $\sphere^2$, but also on arbitrary surfaces, we need to define maps on $2$-manifolds and also need to specify which maps have common properties with polyhedra, which we will call polyhedral maps. The definitions in this section closely follow the ones in \cite{brehm2004polyhedralmaps}.
\clearpage
\begin{definition}[Simple graphs]
  A \hdef{simple graph} $G$ is a pair $(V, E)$ of a finite set $V$ and $E \subseteq \begin{psmallmatrix}V\\2\end{psmallmatrix} = \set{{v, v'} : v, v' \in V, v \neq v'}$ (so $G$ is undirected and finite without loops and multi-edges). A \hdef{subgraph} of $G$ is a graph $G' = (V', E')$, such that $V' \subseteq V$ and $E' \subseteq E \cap  \begin{psmallmatrix}V'\\2\end{psmallmatrix}$ and we want to denote this phenomena by $G' \subseteq G$. A \hdef{path} in $G$ is a subgraph $G_P = (V_P, E_P)$ of $G$, such that $V_P = \set{v_1, \dots, v_k}$ and $E_P = \bigcup_{i = 1}^{k-1}\set{v_i, v_{i+1}}$ for all $i \in \set{1, \dots k - 1}$. A \hdef{cycle} in $G$ is a subgraph $G_C = (V_C, E_C)$ of $G$, such that $V_C = \set{v_1, \dots, v_k}$ and $E_C = \set{v_k, v_1} \cup \bigcup_{i = 1}^{k-1}\set{v_i, v_{i+1}}$. We want to write $v_1 - \dots - v_k$ for paths and $v_1 - \dots - v_k - v_1$ for cycles. The \hdef{valence} of a vertex is the number of adjacent edges.
\end{definition}

\begin{definition}[Embedding of a graph] \todo{Make \phi injective!} Let $G = (V, E)$ be a finite graph (undirected, possibly with loops and multi-edges). An \hdef{embedding} $\phi$ of $G$ into a (topological) $2$-manifold $S$ is a function which assigns to every vertex $v \in V$ a single point $\phi(v) \in S$ and every edge $e = \{v, v'\} \in E$ a subset $\phi(e) \subseteq S$ and a homeomorphism $\phi_e : [0, 1] \stackrel{\cong}{\longrightarrow} \phi(e)$, such that $\phi_e(\set{0, 1}) = \set{\phi(v), \phi(v')}$ and for any two edges $e, e' \in E, e \neq e'$: $\phi_e(\,(0,1)\,) \cap \phi_{e'}(\,(0,1)\,) = \emptyset$ and all vertices $w \in V$: $\phi(w) \not\in \phi_e(\,(0,1)\,)$. We call a graph \hdef{planar} if such an embedding exists into to the Euclidean plane. The closures of the connected components of $S \setminus \bigcup_{e \in E} \phi(e)$ are called \hdef{faces} of the embedding and the set of all faces shall be $F$. We can define an incidence structure between $F$ and $E$ by saying $f \in F$ contains $e \in E \iff f \cap \phi(e) = \phi(e)$, which extends to an incidence poset between $V$, $E$ and $F$ using additionally the normal incidence structure in the graph $G$. To each embedding we can define a \hdef{dual} embedding, where adjacent faces are connected by edges, and the vertices form the new faces.
\end{definition}

\begin{definition}[Map on a closed $2$-manifold] \label{def:map} An embedding of a graph $G$ into a closed $2$-manifold with vertices $V$, edges $E$ and faces $F$ is called a \hdef{map}, provided the following properties hold:
  \begin{itemize}
  \item $G$ is simple,
  \item every vertex $v \in V$ has valence at least $3$ and
  \item every $f \in F$ is a closed $2$-cell (i.e. homeomorphic to $\set{(x, y) \in \reals^2 : x^2 + y^2 \leq 1}$).
  \end{itemize}
  When talking about a map $P$, the underlying graph is called the \hdef{$1$-skeleton} or simply the graph of $P$. The faces of a map incident to $n$ edges (or, equivalently, $n$ vertices) will be called \hdef{$n$-gonal} faces or simply \hdef{$n$-gons}.
\end{definition}

\begin{remark}
  In \autoref{sec:construction} we weaken this definition to some extent to allow for $2$-valent vertices. This does not warrant a whole new definition, so we state it here for completeness and to avoid confusion.
\end{remark}

\begin{definition}[Polyhedral map] \label{def:polymap} A map on a closed $2$-manifold is called \hdef{polyhedral}, if for every two faces $f, f', f \neq f'$ there is either no vertex, a single vertex or a single edge incident to both $f$ and $f'$. In this case the two faces are said to meet properly. \todo{Disambiguate}
\end{definition}

\begin{remark} Planar graphs are exactly those with embeddings into the sphere $\sphere^2 \defeq \set{(x, y, z) \in \reals^3 : x^2 + y^2 + z^2 = 1}$. Embeddings into the sphere and into the plane can be transformed into each other using the stereographic projection (i.e. the map $\psi: \sphere^2 \setminus \set{(0, 0, 1)} \to \reals^2, (x, y, z) \mapsto (\frac{x}{1-z}, \frac{y}{1-z})$) and its inverse, where the projection center (the point $(0, 0, 1)$) on the sphere is neither a vertex nor lies on an edge. We also want to explicitly define (polyhedral) maps on the Euclidean plane as those embeddings which come from stereographic projections of (polyhedral) maps on the sphere.
\end{remark}

\begin{remark}\label{rem:edge:incidence} The incidence poset of a polyhedral map has the property that each edge contains exactly two vertices and is contained in exactly two faces. The first assertion is trivial to see, as we only allowed simple graphs in the definition of polyhedral maps. To see the second fact, first note that by the topology of a closed $2$-manifold each edge $e$ is contained in some face and not in more than two faces. But $e$ can not be contained in a single face $f$ twice, because then $f$ is either not a closed $2$-cell or we would have a situation where $e$ points inwards into $f$ (\autoref{fig:example:pointyface}) in which case the graph contains a vertex of valence $1$.

  \begin{tikzfigure}{\label{fig:example:pointyface}}{Two situations which cannot occur in maps.}
    \matrix (m) [ column sep=1cm] {
      \begin{scope}
        \node (e) at (0.7, 1) [above] {$e$};
        \node (f) at (1, 0.5) {$f$};
        \draw (2,1.75) arc (90:270:0.375 and 0.75);
        \draw (2,1.75) arc (90:-90:0.375 and 0.75);
        \draw (0, 2) arc (90:270:0.5 and 1);
        \draw[dashed] (0, 2) arc (90:-90:0.5 and 1);
        \draw[dotted] (0, 2) -- (2, 1.75);
        \draw[dotted] (0, 0) -- (2, 0.25);
        \draw(-0.5, 1) -- (1.625, 1);
        \fill [black] (-0.5, 1) circle (2pt);
        \fill [black] (1.625, 1) circle (2pt);
        
      \end{scope}
      &
      \begin{scope}
        \node (f) at (1, 0.5) {$f$};
        \node (e) at (1.125, 1) [above] {$e$};
        \draw (1.8, 1) -- (2, 1) -- (2, 2) -- (0, 2) -- (0, 0) -- (2, 0) -- (2, 1);
        \draw[loosely dotted] (1.4, 1) -- (1.8, 1);
        \draw (1.4, 1) -- (1, 1);
        \fill [black] (0, 0) circle (2pt);
        \fill [black] (0, 2) circle (2pt);
        \fill [black] (2, 2) circle (2pt);
        \fill [black] (2, 0) circle (2pt);
        \fill [black] (2, 1) circle (2pt);
        \fill [black] (1, 1) circle (2pt);
        \fill [black] (1.25, 1) circle (2pt);
      \end{scope} 
      \\};
  \end{tikzfigure}
\end{remark}

\begin{remark}
  Because of \autoref{rem:edge:incidence}, the concept of a map and a polyhedral map dualize perfectly, i.e. the dual of a map is again a map and this is also the case for polyhedral maps.
\end{remark}

\begin{remark}\label{rem:polymap:from:polyhedron}
  We can view every polyhedron as a map on a surface, where the graph of the map is the graph / $1$-skeleton of the polyhedron and the embedding is held by ``deforming'' the polyhedron into a sphere $\sphere^2$. In this context each face of the polyhedron corresponds to one in the map. It is easy to see that this map is polyhedral, which gives rise to properties name.
\end{remark}

We want to show that the converse is also true and that polyhedral maps on the sphere $\sphere^2$ and polyhedra have the same $1$-skeletons. For this we need a property from graph theory.

\begin{definition} A graph is called \hdef{$k$-(vertex)-connected} if it has more than $k$ vertices and the deletion of less than $k$ vertices leaves the graph connected.
\end{definition}

\begin{proposition} Every graph $G = (V, E)$ of a polyhedral map $\phi$ \todo{maps are called $M$} is $3$-connected.
  \begin{proof}
    As before call $F$ the set of faces and call $S$ the closed $2$-manifold $\phi$ maps into. First we have to show that $|V| \geq 4$. This is easy to see, since the smallest simple graph (with the least number of vertices) where each vertex has valence at least $3$ is the graph $K_4$ which has $4$ vertices. Second we want to show that if we delete two vertices from $G$ the graph remains connected. Let $G' = (V', E')$ be a graph held from $G$ by removing a single vertex $v'$ and $G'' = (V'', E'')$ be a graph in which also a second vertex $v''$ has been deleted. We can induce from $\phi$ two embeddings $\phi'$ and $\phi''$ from $G'$ and $G''$ into $S$ by $\phi' = \phi|_{G'}$ and $\phi'' = \phi|_{G''}$. To see that $G''$ is connected, assume the contrary and let $f' = \bigcup_{v' \in f \in F} f$. The face $f'$ is homeomorphic to a closed $2$-cell since all faces $f \in F$ containing $v'$ meet in a common vertex (exactly in $v'$) and therefore can not meet in another vertex which has no edge to $v'$. As $v'$ disconnects $G'$ it has edges to at least two connected different components of $G'$, therefore the boundary of $f'$ also contains vertices of at least two connected components. But the boundary of $f'$ is homeomorphic to $\sphere^1$ and thus connected and so the two connected components were actually a single component, contradicting the assumption. To see that $G''$ is connected, too, we again note that $v'$ has to have edges to at least two different connected components, or else there is no difference in deleting $v'$ from $G$ and $G$ would be $1$-connected which we already disproved. Using the same argument as above we again have that $f' = \bigcup_{v' \in f \in F} f$ is homeomorphic to a $2$-cell and that the boundary contains two vertices from different connected components. Since the boundary of $f'$ remains connected even after deleting the additional vertex $v''$, we have held a contradiction.
  \end{proof}
\end{proposition}

\begin{theorem}[{\sc Steinitz}'s theorem, \cite{ConvexPolytopes}] A graph is the $1$-skeleton of a polyhedron if and only if it is $3$-connected and planar.
\end{theorem}

With these two results (and the knowledge that planarity of a graph is equivalent to the embedability into the sphere $\sphere^2$) we can see that in fact every polyhedral map on the sphere $\sphere^2$ comes from a polyhedron and vice versa, at least when looking at the underlying graphs. Actually checking that going from a map to the underlying graph, then to the polyhedron by {\sc Steinitz}'s theorem and back to polyhedral map using \autoref{rem:polymap:from:polyhedron} yields the same map (up to a homeomorphism on the embedding) and the same the other way around will be left out here.

In the rest of the section we want to review two very broad {\sc Eberhard} theorems for polyhedral maps on oriented closed $2$-manifolds. To state them easily we need a few more definitions.

\begin{definition}[Sequence]
  In this thesis we will refer to a \hdef{sequence} $a$ as a map $\nats \setminus \{0, 1, 2\} \rightarrow \nats$ with finite support. These maps will be written as $(a_3, a_4, ..., a_k)$, where $k = \operatorname{max} \operatorname{supp} a$. If $a$ has a small but wide support this notation will be further abbreviated by $[a_{k_1} \times k_1, a_{k_2} \times k_2, ...]$, where only entries not equal to zero occur. Further $a_k \times k$ will be simply written as $k$ if $a_k = 1$. Additionally, we want to define addition and subtraction of two sequences and multiplication with scalars, these operations are to be executed element-wise.
\end{definition}
\begin{example}
  $(2, 0, 0, 1)$, $[2 \times 3, 1 \times 6]$, $[2 \times 3, 6]$ and $2 \cdot [3] + [6]$ all denote the same sequence.
\end{example}
\begin{definition}[$p$-vector and $v$-vector of a map on a surface]\label{def:relizable}
  The \hdef{$p$-vector} of a map $M$ on a $2$-manifold is the sequence $(p_3, \dots, p_m)$, where $p_k$ denotes the number of faces with exactly $k$ vertices. Similarly the \hdef{$v$-vector} of $M$ is the sequence $(v_3, \dots, v_n)$ where each $v_k$ is the number of vertices of $M$ with valence $k$.
\end{definition}

\begin{definition}\label{def:realizable}
  A pair of sequences $p = (p_3, \dots, p_m)$, $v = (v_3, \dots, v_n)$ is said to be \hdef{realizable as a polyhedral map} on the closed $2$-manifold $S$ (or short: realizable on $S$), if there exists such a map having $p$ as its $p$-vector and $v$ as its $v$-vector.
\end{definition}

The two main theorems we want to base our constructions on are the following:

\begin{theorem}[{\sc Jendrol', Jucovi{\v{c}}}, 1977, \cite{jendrol1977generalization}] \label{thm:eberhard:extended:3}
  Each pair of sequences $p = (p_3, \dots, p_m)$ and $v = (v_3, \dots, v_n)$ is realizable on the closed orientable $2$-manifold with {\sc Euler}-characteristic $\chi$ for some $p_6 \in \nats$, $v_3 \in \nats$ if and only if
  \begin{align*}
    \sum_{k=3}^m (6-k)p_k + 2 \sum_{k=4}^n (3-k)v_k &= 6\chi, \\
    \sum_{k=3 \atop 2 \nmid k}^{m} p_k \neq 0 \text{ or} \sum_{k=4 \atop 3 \nmid k}^n v_k &\neq 1 &\text{ if } \chi = 2, \\
    p \neq [5, 7] \text{ or } v \neq [v_3 \times 3]  &&\text{ if } \chi = 0.
  \end{align*}
\end{theorem}

\begin{theorem}[{\sc Jendrol', Jucovi{\v{c}}, Barnette, Grünbaum, Zaks}, 1973, \cite{jucovivc1973theorem}, \cite{barnette1971toroidal}, \cite{grunbaum1969planar}, \cite{zaks1971analogue}] \label{thm:eberhard:extended:4}
  Each pair of sequences $p = (p_3, \dots, p_m)$ and $v = (v_3, \dots, v_n)$ is realizable on the closed orientable $2$-manifold with {\sc Euler}-characteristic $\chi$ for some $p_4, v_4 \in \nats$ if and only if
  \begin{align*}
    \sum_{k=3}^m (4-k)p_k + \sum_{k = 3}^n (4-k)v_k &= 4\chi, \\
    \sum_{k=3 \atop k \neq 4}^m k p_k &\equiv 0& (\mod 2), \\
    p \neq [3, 5] \text{ or } v \neq [v_4 \times 4] &&\text{ if } \chi = 0,\\
    p \neq [p_4 \times 4] \text{ or } v \neq [3, 5] &&\text{ if } \chi = 0.
  \end{align*}
\end{theorem}

Another good argument why these theorems fail on the torus in some cases can be found in \cite{izmestiev2013there}.